Letter to Reviewers of Submission \#341

### 2015-06-27 casestudies.tex
within page limits! still writing revision letter

\begin{figure*}
  \includegraphics[width=\linewidth]{fig/casestudytext/casestudytext.pdf}
  \caption{\label{fig:textvis}An example application developed and deployed in RCloud.}
\end{figure*}

>>>>

\begin{figure*}
  \vspace{-1.5em}
  \includegraphics[width=\linewidth]{fig/casestudytext/casestudytext.pdf}
  \vspace{-3.0em}
  \caption{\label{fig:textvis}LDAVis, an example application developed
    and deployed entirely in RCloud.  LDAVis allows analysts to
    visually explore \emph{topic models}, statistical
    representations of different topics in a document collection.
  }\vspace{-1.5em}
\end{figure*}

### 2015-06-27 discussion.tex
within page limits! still writing revision letter

\begin{table}
  \centering
  \begin{tabular}{l|cccccc}
    & V/F & C & D & ML & R & A \\
    \hline
RCloud     &       x            &       x       &     x      &      x        &           x        &           x         \\
RStudio    &                    &               &            &               &           x        &           x         \\
JSFiddle   &       x            &       x       &            &               &                    &                     \\
bl.ocks    &       x            &       x       &            &               &           x        &                     \\
shiny      &                    &               &     x      &               &           x        &           x         \\
Jupyter    &                    &               &            &      x        &           x        &           x         \\
Tableau    &                    &      x        &     x      &               &           x        &                     \\
ManyEyes   &                    &      x        &     x      &               &                    &                     
  \end{tabular}
  \caption{Comparison of system features. Columns: Versioning/Forking, Collaboration, Deployment, Multi-language support, Integrated Reports, and Integrated Analysis.}
\end{table}

@@

Experience with deploying RCloud in a community of data analysts
(``hackers'') gave us some insight into whether the proposed
requirements were appropriate, and were met.

Our experience underscored the relevance of Heer and Agrawala's design
considerations, and indicated areas for further exploration. We adopt
their taxonomy in the following discussion.

>>>>

\begin{table}
  \centering
  \begin{tabular}{l|cccccc}
    & V/F & C & D & ML & R & A \\
    \hline
RCloud     &       x            &       x       &     x      &      x        &           x        &           x         \\
RStudio    &                    &               &            &               &           x        &           x         \\
JSFiddle   &       x            &       x       &            &               &                    &                     \\
bl.ocks    &       x            &       x       &            &               &           x        &                     \\
shiny      &                    &               &     x      &               &           x        &           x         \\
Jupyter    &                    &               &            &      x        &           x        &           x         \\
Tableau    &                    &      x        &     x      &               &           x        &                     \\
ManyEyes   &                    &      x        &     x      &               &                    &                     
  \end{tabular}
  \caption{Summary of features for similar systems. The columns stand for, respectively, Versioning/Forking, Collaboration, Deployment, Multi-language support, Integrated Reports, and Integrated Analysis.}
\end{table}

@@

Experience with deploying RCloud in a community of data analysts
(``hackers'') gave us some insight into whether the proposed
requirements were appropriate, and were met.
%
Our experience underscored the relevance of Heer and Agrawala's design
considerations, and indicated areas for further exploration~\cite{Heer:2008:DCF}. We adopt
their taxonomy in the following discussion.

### 2015-06-27 introduction.tex
accidentally duplicated text
within page limits! still writing revision letter

Results of experiments are often shared first by copying screen
shots or static output. By the time decisions are made based on
the results of that screenshot, data and processes may have changed
so much that the decision can be wrong.

@@

Fortunately, there is abundant evidence that technology can
solve many of these problems.
Gutierrez's interviews with data scientists~\cite{Gutierrez:2014:DSA}, 
include the following:

\begin{itemize}
\item (upon being given access to other code and data analysis, in
order to learn about Hadoop) ``I could look at other people’s code
and play with their code and data sets as well''
\item (discussing the value of sharing prototypes rather than static
data) ``Prototyping our products so that internal
customers can use them early on has been crucial for
our success. Now we can shoot off a URL to internal
customers and it allows them to provide feedback way before
we're talking about getting it into production.''
\item (on sharing more than just a finished product) ``We also share
exploratory analyses and reports so that we can still exchange
knowledge even if the work didn't make it into a larger project.''
\item (on changing analyses and processes) ``It is important to
have testing frameworks so you can go back and test all
of your data.''
\end{itemize}

>>>>

@@

%% Fortunately, there is abundant evidence that technology can
%% solve many of these problems.
%% Gutierrez's interviews with data scientists~\cite{Gutierrez:2014:DSA}, 
%% include the following:

%% \begin{itemize}
%% \item (upon being given access to other code and data analysis, in
%% order to learn about Hadoop) ``I could look at other people’s code
%% and play with their code and data sets as well''
%% \item (discussing the value of sharing prototypes rather than static
%% data) ``Prototyping our products so that internal
%% customers can use them early on has been crucial for
%% our success. Now we can shoot off a URL to internal
%% customers and it allows them to provide feedback way before
%% we're talking about getting it into production.''
%% \item (on sharing more than just a finished product) ``We also share
%% exploratory analyses and reports so that we can still exchange
%% knowledge even if the work didn't make it into a larger project.''
%% \item (on changing analyses and processes) ``It is important to
%% have testing frameworks so you can go back and test all
%% of your data.''
%% \end{itemize}
